Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-07-26 article_springer/article_springer.Rmd
typos

$$
\underset{x\rightarrow \infty}{lim}\frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
$$

For more details regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.

@@

: For the magnitudes $J_k$ assumption \eqref{assumptionJs} holds. Furthermore, let the waiting times $W_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
\begin{align} \label{eq:stability}
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
\end{align}
for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$, $s > 0$. Write $p_{\ell} := \mathbf P(J > \ell)$. Then the weak convergence
$$
\frac{T(\ell)} {b(1/p_{\ell})} \to Z_\beta \quad \text{ as } \quad \ell \uparrow x_R
$$
holds, where the Mittag-Leffler random variable $Z_\beta$ is defined on 
the positive real numbers via 
$$
\mathbf E[\exp(-sZ_\beta)] = \frac{1}{1+s^\beta}.
$$

>>>>

$$
\lim_{x \to \infty} \frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
$$

For more details on regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.

@@

: For the magnitudes $J_k$, let assumption \eqref{assumptionJs} hold. Furthermore, let the waiting times $W_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
\begin{align} \label{eq:stability}
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
\end{align}
for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$, $s > 0$. Write $p_{\ell} := \mathbf P(J > \ell)$. Then the weak convergence
$$
\frac{T(\ell)} {b(1/p_{\ell})} \to Z_\beta \quad \text{ as } \quad \ell \uparrow x_R
$$
holds, where the Mittag-Leffler random variable $Z_\beta$ is defined on 
the positive real numbers via 
$$
\mathbf E[\exp(-sZ_\beta)] = \frac{1}{1+s^\beta}.
$$
